Self Regulation Ontology Retest Analyses

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem figures

mean_diff_df %>%
  left_join(valence_df, by = c("dv", "task")) %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
  group_by(task) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
  gather(key, value, -task) %>%
  mutate(total_vars = c(74, 372, 74, 372),
         prop = value/total_vars) %>%
  ggplot(aes(key, prop, group=task, fill=task))+
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
  theme(legend.title = element_blank())+
  xlab("")+
  ylab("Proportion")+
  ylim(0, 1)+
  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
                   labels = c("Self-control decrease", "Self-control increase"))

ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 5, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))

@@

write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
```

```{r warning=FALSE, message=FALSE}
# trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))

@@

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```

>>>>

mean_diff_df %>%
  left_join(valence_df, by = c("dv", "task")) %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
  group_by(task) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
  gather(key, value, -task) %>%
  mutate(total_vars = c(74, 372, 74, 372),
         prop = value/total_vars) %>%
  ggplot(aes(key, prop, group=task, fill=task))+
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("Proportion")+
  ylim(0, 1)+
  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
                   labels = c("Self-control decrease", "Self-control increase"))

ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r eval=FALSE}
hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))

@@

# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
```

```{r warning=FALSE, message=FALSE}
trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))

@@

tmp2 %>%
  filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  # facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

ggsave('PointEst_DDM_Comp_OverallOnly.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 5, units = "in", limitsize = FALSE)
```
